Analysing the Performance of Shallow-Water Models with the Roofline Model

### 2017-01-24 docs/papers/roofline_habakkuk/habakkuk.tex
habakkuk paper: add figure and update data for mulsd/divsd overlap

Obtaining a performance estimate by simply counting all of the FLOPs
that must be performed is equivalent to assuming that they are all
executed sequentially. However, a core on any recent generation of CPU
is likely to have support for Instruction Level Parallelism.

>>>>

Obtaining a performance estimate by simply counting all of the FLOPs
that must be performed is equivalent to assuming that they are all
executed sequentially. However, a core on any recent generation of CPU
is likely to have support for Instruction Level Parallelism. For
instance, in Intel Ivybridge micro-architecture a core has six
execution ports to which micro-operations are
despatched. Floating-point multiplication and division is handled by
port 0 while addition is handled by port 1.

\begin{figure}
\includegraphics[width=130mm]{mulsd_divsd}
\caption{Cost in cycles on an Intel E5-1620 v.2 CPU of the inner-loop
  body as a function of number of independent MULSD and DIVSD
  instructions.}
\label{FIG_mul_div_overlap}
\end{figure}
